
Description of the quasi-crystalline datastore.

It’s a quasi‑crystalline datastore where storage, logic, and computation share the same substrate.
There is no separation between data and execution.
The datastore enforces deterministic consensus using modular arithmetic instead of probabilistic smoothing.


# 📙 **Paper 4 (Time and Dimensions)**  
**Include the full conceptual version.**

This is where you will:

- redefine time as discrete execution  
- define the coherence‑velocity as the true temporal constant  
- show how the M46 manifold maintains shape across time  
- show how dimensionality emerges from execution order  
- show how the universe’s “clock rate” is c/137  

This is the *proper home* for the deeper theory.


## **Time as the Execution Rate of the Lattice**

In the SpaceTCO framework, time is not a continuous dimension. It is the discrete execution of the lattice’s state‑change. The universe updates itself at a finite rate, and this rate defines the **speed of coherence**:

\[
v_{\text{coh}} = \frac{c}{137}.
\]

This is the maximum velocity at which the Generator Field can propagate consensus. It is the true temporal constant of the universe.

### **1. The Proximity‑Snap Potential**

The Proximity‑Snap potential is the temporal mechanism by which decohered structures are re‑captured. A jittering region propagates outward at \(v_{\text{coh}}\) until it enters the influence zone of a stable prime‑sector minimum. At that moment, the lattice executes a deterministic snap, truncating excess information and restoring coherence.

### **2. Dimensional Stability**

Because coherence propagates at a finite rate:

- the M46 manifold maintains its shape,  
- the 12‑Prime Fan remains rigid,  
- the 60‑unit bandwidth remains invariant,  
- the Iso‑Pi Horizon remains well‑defined.

Dimensionality is therefore not a background property.  
It is the emergent result of a finite execution rate.

### **3. The Universe as a Temporal Processor**

The universe is not a continuous spacetime manifold.  
It is a **temporal processor** executing:

1. tension redistribution,  
2. phase realignment,  
3. identity preservation  

at a finite rate.

The speed of light is not the fundamental limit.  
The speed of coherence is.
